ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images

### 2023-02-11 paper/paper.tex
update sample patch images, update subsection title

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth, frame]{figures/matrix.png}
\caption{Sample patches from \emph{ShabbyPages}.} \label{fig1}
\end{figure}

@@

@@

\subsection{Processing \emph{Augraphy} on a multicore system}
Execution time is dependent on which augmentations are executed at runtime; a long \emph{Augraphy} pipeline can take several seconds to process large images.
The library is under active development with performance enhancements underway, but the time cost to generate large datasets sequentially is prohibitive when dealing with thousands of files, so we use a multi-process pooling technique to distribute the workload across many processor execution threads.
For each process, a new pipeline with new probability coefficients was generated, representing a nontrivially-different sequence of document operations.
Each of the 6202 base images was passed through a unique pipeline, with the output saved to a separate directory.
\emph{Augraphy}'s API design made it very easy to write the code to accomplish this; the entire \emph{ShabbyPages} generation script is fewer than 30 lines long including imports, with the most critical piece represented below:

>>>>

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth, frame]{figures/quad.png}
\caption{Sample patches from \emph{ShabbyPages}.} \label{fig1}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=1.0\textwidth]{figures/matrix_tall1.png}
    \caption{Sample noisy patches from ShabbyPages.}
    \label{fig:matrix_tall1}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=1.0\textwidth]{figures/matrix_tall2.png}
    \caption{Sample noisy patches from ShabbyPages.}
    \label{fig:matrix_tall2}
\end{figure}

\subsection{Processing \emph{Augraphy} Pipelines}
Execution time is dependent on which augmentations are executed at runtime; a long \emph{Augraphy} pipeline can take several seconds to process large images.
The library is under active development with performance enhancements underway, but the time cost to generate large datasets sequentially is prohibitive when dealing with thousands of files, so we use a multi-process pooling technique to distribute the workload across many processor execution threads.
For each process, a new pipeline with new probability coefficients was generated, representing a nontrivially-different sequence of document operations.
Each of the 6202 base images was passed through a unique pipeline, with the output saved to a separate directory.
\emph{Augraphy}'s API design made it very easy to write the code to accomplish this; the entire \emph{ShabbyPages} generation script is fewer than 30 lines long including imports, with the most critical piece represented below:
